The Cal Poly Spacecraft Attitude Dynamics Simulator (SADS) is an ongoing project to develop  an air-bearing platform capable of recreating on-orbit rotational dynamics with near frictionless and torque-free rotations. However, any offset between the platform's center of rotation and its center of mass will introduce a torque due to gravity. This thesis presents the design, implementation, and experimental evaluation of a low-cost, automatic mass balancing system for the SADS to address this challenge.

A new modular sliding mass system was developed that overcomes issues faced in previous iterations of the SADS, providing real-time positional control of the masses and a customizable center of mass envelope. An STM32-based onboard computer was developed that implements control laws, balancing algorithms, and attitude estimation using a combination of Simulink code generation and C/C++ drivers. A variety of balancing methods found in literature are tested experimentally including active feedback control, least-squares batch estimation, and Kalman filtering. The best balancing results are obtained using a PID controller to compensate for the horizontal imbalance, and an unscented Kalman filter for the vertical imbalance. This approach reduces the torque due to gravity to the order of \SI{e-4}{\newton\meter}, which aligns with results achieved by comparable simulators at other universities. This work additionally contributes to the literature by demonstrating an experimental PID-based balancing approach and benchmarking its performance against alternative methods.
